Untitled

### 2021-08-10 Main_Figures/Global_trait_spectrum.Rmd
Update on labels and x-y axes of Figure 1

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(cowplot)
# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.2)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(1.2, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}

@@

  plot <- plot + xlab(paste("PC1 ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("PC2 ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
     annotation_raster(style_l_1, xmin = 2.05, xmax = 2.85,ymin = 2.35, ymax = 3.5) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 1.8, ymax = 4.5) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2.1, ymax = -1.60) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

      #ADD LABELS
  rownames(PC$L) <- c("Selfing", "Flower number", "Flower Size", "Style length", "Ovule number", "Plant height" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.6,4.95,5.5,7.25,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.4,3,6.2,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4)

>>>>

#Load libraries
#LOAD LIBRARIES
library(phytools)
library(ape) #for phylogenetic distance
library(dplyr) #data processing
library(rtrees) #for phylogenetic distancelibrary(MASS)
library(reshape2)
library(viridis) #COLOUR GGPLOT
library(MASS)
library(ggplot2)
library(broman) #crayon colours
library(cowplot)
# Theme for publication
theme_ms <- function(base_size=12, base_family="Helvetica") {
  (theme_bw(base_size = base_size, base_family = base_family)+
      theme(text=element_text(color="black"),
            axis.title=element_text( size = rel(1.75)),
            axis.text=element_text(size = rel(1.75), color = "black"),
            legend.title=element_text(face="bold"),
            legend.text=element_text(),
            legend.background=element_rect(fill="transparent"),
            legend.key.size = unit(1.2, 'lines'),
            panel.border=element_rect(color="black",size=1),
            panel.grid.minor.x =element_blank(),
            panel.grid.minor.y= element_blank(),
             panel.grid.major= element_blank()
      ))
}

@@

  plot <- plot + xlab(paste("Flower number - flower size trade-off ", "(",(percentage[1]),"%",")", sep = "")) #XLAB
  plot <- plot + ylab(paste("Pollinator dependence trade-off ", "(",(percentage[2]),"%",")", sep = "")) #YLAB

@@

  plot <- plot + theme_bw() + annotation_raster(tree_1, xmin = -4.1, xmax = -2.85,ymin = 2.05, ymax = 4.05)+
     annotation_raster(style_l_1, xmin = 2.25, xmax = 3.05,ymin = 2.55, ymax = 3.7) +
    annotation_raster(style_s_1, xmin = -2.6, xmax = -1.9,ymin = -2.65, ymax = -1.7) +
    annotation_raster(ovule_h_1, xmin = 3.5, xmax = 4.2,ymin = -0.45, ymax = 0.50) +
    annotation_raster(ovule_l_1, xmin = -4.2, xmax = -3.5,ymin = -0.45, ymax = 0.5) +
    annotation_raster(selfing_n_1, xmin = -0.75, xmax = 1.2,ymin = 2, ymax = 4.7) +
    annotation_raster(selfing_h_1, xmin = -0.30, xmax = 0.15,ymin = -3.9, ymax = -3.1) +
    annotation_raster(single_flower_1, xmin = 3.3, xmax = 4.1,ymin = -1.7, ymax = -0.7) +
    annotation_raster(many_flowers_1, xmin = -4.20, xmax = -3.40,ymin = 0.8, ymax = 1.45) +
    annotation_raster(large_flower_1, xmin = 3.15, xmax = 4.15,ymin = 1.3, ymax = 2.55) +
    annotation_raster(flower_small_1, xmin = -3.50, xmax = -2.55,ymin = -2, ymax = -1.50) +
    annotation_raster(herb_1, xmin = 2.6, xmax = 3,ymin = -2.8, ymax = -2)

      #ADD LABELS
  rownames(PC$L) <- c("High selfing", "Many flowers", "Large flowers", "Long styles", "Many ovules", "Tall plants" )

  PCAloadings <- data.frame(Variables = rownames(PC$L), PC$L)
 plot <- plot + annotate("text", x = -(PCAloadings$PC1*c(4.7,5.05,5.6,7.85,7.3,6.15)), y = -(PCAloadings$PC2*c(4.693,2.5,3.1,6.6,5,5.5)+c(0,0,0,0,0.4,0)),
                         label = PCAloadings$Variables, color="black",fontface =2,size=4)

 plot <- plot + annotate("text", x = (PCAloadings$PC1*c(4.6,4.95,4.5,6.6,7.3,5.15)), y = (PCAloadings$PC2*c(3.83,6.4,5.7,7.4,-1,7.45)+c(0,0,0,0,-0.41,0)),
                         label =c("Low selfing", "Few flowers", "Small flowers", "Short styles", "Few ovules", "Short plants" ), color="black",fontface =2,size=4)
